\chapter{Requirements and Analysis}\label{ch:requirements-and-analysis}

\section{Aims and Objectives}\label{sec:aims-and-objectives2}

The following subsections shall detail the aims and objectives of this dissertation project.

\subsection{Demonstrate Age-Related Deviations in Speech}\label{subsec:aim1}

As presented in the literature review, age is understood to have an impact on the structure of
speech, thus an aim of this work is to better visualise and collate this understanding using
frequency spectra and searching for deviations in speech across multiple large speech corpora.

An example experiment to visualise age-related deviations in speech may consist of using ASR to
isolate occurrences of the same word across speech corpora, then comparing frequency spectra
across recordings.

\subsection{Present the Purpose of Improving ASR for the Elderly}\label{subsec:aim1andahalf}

This report has presented the problem of poor ASR performance for elderly speakers, but hasn't
presented the real benefits of improving such systems.
To improve the flow of the final project, a section should present the reason why it is an
important area of research and how it would produce human benefit.

To aid understanding, it may be worth also presenting how elderly peoples' lives are negatively
affected as a result of poor or unreliable ASR performance.
This would create a real understanding as to why this field should be considered more in current
research.

\subsection{Compare the Effectiveness of Different ASR Models on Elderly Speech}\label{subsec:aim2}

This objective requires either a series of ASR systems to use to obtain experimental results, or
instead highly detailed, full transcription results across common speech corpora which contain
elderly speakers.
Accessing these resources may be difficult because many ASR systems aren't available to be used
freely and the full results present in their literature are often unpublished.

\subsection{Present an Understanding of Contemporary ASR Systems}\label{subsec:aim2andahalf}

An area of great complexity not covered in significant detail in this preliminary report is the
architecture of an ASR system.
While two existing systems are presented, the final project would benefit from a diagrammatic
exploration of how these systems are formed, what the purpose of each section is, and what the
differences between models mean.

A diagram featured in the work of Radford et al.\cite{whisper} provides the reader a potent, while
relatively easily understood knowledge of how their model functions.
Presenting various models in a similar fashion would enable a reader to gain a straightforward and
accessible understanding of how these models differ, and why these differences matter.

\subsection{Experimentally Alter ASR Models}\label{subsec:aim3}

In~\ref{sec:bespoke-systems}, the potential benefit of altering an existing ASR system was
discussed.
Though it may be difficult, the potential benefit to the work of the Clarity project means that
this is a relevant and important objective, at least so far as performing experiments to test the
viability of such a method.

\subsection{Produce Suggestions to Improve ASR Performance for Elderly Speakers}\label{subsec:aim4}

Using findings from the previous objectives, this work aims to provide suggestions to those
interested in the furthering of ASR technology as it relates to transcribing elderly and less
common speech patterns.
This objective is very important because there is a clear disparity in the accuracy of ASR
transcriptions for elderly speakers and a distinct lack of interest from contemporary researchers
made apparent by this disparity.