\section{Project Plan}\label{sec:proj-plan}

To allow for enhanced flexibility, the plan is split into five ordered chunks;
each should last approximately two weeks but are intended to be adaptable.

\subsection{Chunk 1}\label{subsec:wk1}

\begin{itemize}
    \item Move LifeLUCID onto Bessemer.
    \item Install wav2vec 2.0 on Bessemer.
    \item Experiment with wav2vec to gain familiarity.
    \item Improve efficiency of batch transcription tasks by reading over the HPC literature.
    \item Write Python scripts to enable WER \& PER calculation from ASR-generated transcripts.
    \item Search for further corpora and open-source ASR systems relevant to the project.
\end{itemize}

\subsection{Chunk 2}\label{subsec:wk2}

\begin{itemize}
    \item Review literature to gain a less ASR-focused understanding of speech irregularities and
    how they relate to age.
    Use spectral analysis and other signal processing techniques to produce examples of these
    characteristics.
    \item Collect results to compare existing ASR systems across corpora with a focus on
    age-related performance.
    \item Present an analysis of these results.
\end{itemize}

\subsection{Chunk 3}\label{subsec:wk3}

\begin{itemize}
    \item Research the adaptation and fine-tuning of ASR models.
    \item Experimentally fine-tune existing models.
    \item Compare the results of fine-tuned models to the literature.
\end{itemize}

\subsection{Chunk 4}\label{subsec:wk4}

\begin{itemize}
    \item Suggest age-related areas of improvements for ASR\@.
    \item Write a detailed analysis of findings.
\end{itemize}

\subsection{Chunk 5}\label{subsec:wk5}

\begin{itemize}
    \item Prepare presentation of findings.
    \item Finalise report formatting and quality of writing.
\end{itemize}